---
title: "Assignment 2 - Airbnb prediction models"
subtitle: "Course: ECBS6067 - Prediction with Machine Learning for Economists"
author: "Anne Valder"
date: "2023-12-02"
output:
  pdf_document: default
  html_document:
  df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Data 
```{r}
# Oslo, Dates? Look at Slides Airbnb model 
```

# Task 1
## • Business Your task will be to help a company operating small and mid size apartments hosting 2 6 guests . The company is set to price their new apartments not on the market.
## • Pick a city you will operate in.
## • Build a price prediction model similarly to how we did in our case study for London.
## • Discuss your modeling decisions and compare your results to those of the case study.

### • You may use other variables we used in class,
### • You may do different feature engineering
### • You may make other sample design decisions
### • But document your steps
### • Have 3 different models and compare performance
### • Argue for your choice of models
### • One model must be OLS another must Random Forest or any boosting algorithm , the third could be either or stg different

```{r}

```

# Tasks 2
## • Please pick two dates , one before and one after lockdowns in that city.
## • Carry out the exercise before the lockdown
## • Take your selected model and use it on the post lockdown date
## • Compare the predictive power of the model . Discuss briefly in the report


```{r}

```

# Tasks 3
## • Consider your ML model (RF or Boosting
## • Explain features ’ contribution to predicted values on average , using Shapley values
## • You shall use a SHAP method
## • You may use graphs , but the emphasis is on the discussion part.
## • This is worth relatively few points , do it only if everything else is already done