---
title: "Predicting fast growth"
output: 
  flexdashboard::flex_dashboard:
    theme: journal #  yeti
      #bg: "#101010"
      #fg: "#FDF7F7" 
      #primary: "#ED79F9"
      #base_font: !expr bslib::font_google("Prompt")
      #code_font: !expr bslib::font_google("JetBrains Mono")
    orientation: rows
    version: 4
    #source_code: embed
    vertical_layout: scroll
    #social: ["menu"]
    navbar:
      - {icon: "fa-github", 
         title: "Repository", 
         href: "https://github.com/anneval/DA3-phdma/tree/main/A3", align: right, target: blank}
    runtime: shiny
---



<!-- Task3.1: Use some methods to interpret your random forest probability model (Shapley, PDP) --> 

<!-- Task3.2: Create a shiny (flexdashboard) app for the project where you can show (1) how key variables influence the prediction (!Shapley) and (2) show expected loss based on different thresholds. -->


```{r global setup, include=FALSE}
# Clear memory
rm(list=ls())
# set global chunk options
knitr::opts_chunk$set(include = FALSE, fig.align = 'center', cache = F,
                     warning = FALSE, message = FALSE, echo = FALSE)

options(scipen = 999)
```

```{r md setup, include=FALSE}
# Set options for markdown
knitr::opts_knit$set(root.dir = 'C:/Users/avalder/OneDrive - WU Wien/Documents/Study/WS_23_24/Pred_MLE_Econ/da_case_studies')

# store different directories here:
# C:/Users/thuebel/OneDrive - WU Wien/Docs/06 Courses and Study/02 Prediction with ML for Economists/da_case_studies
# C:/Users/avalder/OneDrive - WU Wien/Documents/Study/WS_23_24/Pred_MLE_Econ/da_case_studies
# C:/Users/AnjaHahn/OneDrive - DataScience Service GmbH/WU/Courses/CEU Prediction with Machine Learning for Economists/da_case_studies
```

<!-- Set directory, load functions and theme  --> 
```{r helper functions, include=FALSE}
#getwd()
source("set-data-directory.R")
source("ch00-tech-prep/theme_bg.R")
source("ch00-tech-prep/da_helper_functions.R")
```

```{r libraries, include=FALSE}
library(flexdashboard)
library(readr)
library(dplyr)
library(tidyr)
library(knitr)
library(ggplot2)
library(readxl)
library(shiny)
library(treeshap)
library(pdp)
library(pROC)
library(plotly)
```

```{r data import,include=FALSE}
data_in <- paste(data_dir,"bisnode-firms", sep = "/")
#load(paste(data_in,"A3.RData",sep = "/")) #activate once we have correct data
load(paste(data_in,"A3_dashboard.RData",sep = "/")) #activate once we have correct data

```
# Variable Importance
#### **Importance of key variables**
### {style="border: 0px; background: none"}
 
## Row {.tabset .tabset-fade}
### Bisnode 
Variable importance all features

```{r, include=T}
##############################
# 3) full varimp plot, above a cutoff
##############################
rf_model_plots$rf_model_plot_all_1
```

###  Manufacturing
Variable importance all features

```{r, include=T}
##############################
# 3) full varimp plot, above a cutoff
##############################
rf_model_plots$rf_model_plot_all_2

```

### Services
Variable importance all features

```{r, include=T}
##############################
# 3) full varimp plot, above a cutoff
##############################
rf_model_plots$rf_model_plot_all_3
```

## Row {.tabset .tabset-fade}
### Bisnode 
Variable importance top 10 
```{r, include=T}
##############################
# 1) full varimp plot, top 10 only
##############################
rf_model_plots$rf_model_plot_10_1

```


###  Manufacturing
Variable importance top 10 
```{r, include=T}
##############################
# 1) full varimp plot, top 10 only
##############################
rf_model_plots$rf_model_plot_10_2
```

### Services
Variable importance top 10 
```{r, include=T}
##############################
# 1) full varimp plot, top 10 only
##############################
rf_model_plots$rf_model_plot_10_3

```


## Row {.tabset .tabset-fade}
### Bisnode 
Variable importance grouped
```{r, include=T}
##############################
# 2) varimp plot grouped to (8)
##############################
# grouped variable importance - keep binaries created off factors together
rf_model_plots_grouped$rf_model_var_imp_grouped_plot1

```


###  Manufacturing
Variable importance grouped

```{r, include=T}
##############################
# 2) varimp plot grouped to (8)
##############################
# grouped variable importance - keep binaries created off factors together
rf_model_plots_grouped$rf_model_var_imp_grouped_plot2

```

### Services
Variable importance grouped

```{r, include=T}
##############################
# 2) varimp plot grouped to (8)
##############################
# grouped variable importance - keep binaries created off factors together
rf_model_plots_grouped$rf_model_var_imp_grouped_plot3
```

# <font size="3">Bisnode</font> {data-navmenu="PDP"}
### {style="border: 0px; background: none"}

## Sidebar {.sidebar}
```{r, include=TRUE}
# Sample list of saved graphs
saved_graphs <- rf_pdp_plot
selectInput("feature_selector", "Select a Feature", choices = names(saved_graphs))

```

Column
-----------------------------------------------------------------------

### Partial dependence plot
```{r, include=TRUE}
renderPlot({
  selected_feature <- input$feature_selector
  print(saved_graphs[[selected_feature]])
})
```
 
# <font size="3">Manufacturing</font> {data-navmenu="PDP"}
### {style="border: 0px; background: none"}

## Sidebar {.sidebar}
```{r, include=TRUE}
# Sample list of saved graphs
saved_graphs <- rf_pdp_plot_manu
selectInput("feature_selector", "Select a Feature", choices = names(saved_graphs))

```

Column
-----------------------------------------------------------------------

### Partial dependence plot
```{r, include=TRUE}
renderPlot({
  selected_feature <- input$feature_selector
  print(saved_graphs[[selected_feature]])
})
```

# <font size="3">Services</font> {data-navmenu="PDP"}
### {style="border: 0px; background: none"}

## Sidebar {.sidebar}
```{r, include=TRUE}
# Sample list of saved graphs
saved_graphs <- rf_pdp_plot_serv
selectInput("feature_selector", "Select a Feature", choices = names(saved_graphs))

```

Column
-----------------------------------------------------------------------

### Partial dependence plot
```{r, include=TRUE}
renderPlot({
  selected_feature <- input$feature_selector
  print(saved_graphs[[selected_feature]])
})
```

# Threshold decision
#### **Expected loss based on different thresholds:**

TEXT 

## Row {.tabset .tabset-fade}
### Bisnode


```{r, include=TRUE}
# re-run losses for RF s.t roc_object is correctly stored
# Now use loss function and search for best thresholds and expected loss over folds -----
rf_model_p_InteractLossPlot
```

### Manufacturing

```{r, include=TRUE}
# re-run losses for RF s.t roc_object is correctly stored
# Now use loss function and search for best thresholds and expected loss over folds -----
rf_model_p_manu_InteractLossPlot
```
### Services
```{r, include=TRUE}
# re-run losses for RF s.t roc_object is correctly stored
# Now use loss function and search for best thresholds and expected loss over folds -----
rf_model_p_serv_InteractLossPlot
```

