---
title: "Predicting fast growth"
output: 
  flexdashboard::flex_dashboard:
    theme: journal #  yeti
      #bg: "#101010"
      #fg: "#FDF7F7" 
      #primary: "#ED79F9"
      #base_font: !expr bslib::font_google("Prompt")
      #code_font: !expr bslib::font_google("JetBrains Mono")
    orientation: rows
    version: 4
    #source_code: embed
    vertical_layout: scroll
    #social: ["menu"]
    navbar:
      - {icon: "fa-github", 
         title: "Repository", 
         href: "https://github.com/anneval/DA3-phdma/tree/main/A3", align: right, target: blank}
  
---

<!-- README:  By default dashboards are standard HTML documents that can be deployed on any web server or even attached to an email message. You can optionally add Shiny components for additional interactivity and then deploy on Shiny Server or shinyapps.io. -->

```{r setup, include=FALSE}
library(flexdashboard)
library(tsbox)
library(dygraphs)
library(readr)
library(dplyr)
library(tidyr)
library(knitr)
library(ggplot2)
library(readxl)
library(stargazer)
library(vars)
```

# <font size="3">Bisnode</font> {data-navmenu="Key variables"}
#### **Importance of key variables**
### {style="border: 0px; background: none"}

TEXT 

```{r}
githubURL <- "https://github.com/anneval/MA_data/blob/main/All.RData?raw=true"
#load(url(githubURL))

load(file(githubURL))
```

## Row {.tabset .tabset-fade}
### Variable importance

```{r}
## 2 or more versions (cutoff, top 10...)
```

-------------------------------------

### Shapley

```{r}

```

-------------------------------------

### Partial dependence plot


```{r}

```

-------------------------------------

# <font size="3">Manufacturing</font> {data-navmenu="Key variables"}
#### **Importance of key variables**
### {style="border: 0px; background: none"}

TEXT 

```{r}
githubURL <- "https://github.com/anneval/MA_data/blob/main/All.RData?raw=true"
#load(url(githubURL))

load(file(githubURL))
```

## Row {.tabset .tabset-fade}
### Variable importance

```{r}
## 2 or more versions (cutoff, top 10...)
```

-------------------------------------

### Shapley

```{r}

```

-------------------------------------

### Partial dependence plot


```{r}

```

-------------------------------------


# <font size="3">Services</font> {data-navmenu="Key variables"}
#### **Importance of key variables**
### {style="border: 0px; background: none"}

TEXT 

```{r}
githubURL <- "https://github.com/anneval/MA_data/blob/main/All.RData?raw=true"
#load(url(githubURL))

load(file(githubURL))
```

## Row {.tabset .tabset-fade}
### Variable importance

```{r}
## 2 or more versions (cutoff, top 10...)
```

-------------------------------------

### Shapley

```{r}

```

-------------------------------------

### Partial dependence plot


```{r}

```

-------------------------------------


# Threshold decision
#### **Expected loss based on different thresholds:**

TEXT 

```{r}
## add model test RF here 


### call results from other sheet 
# source? 
```



## Row {.tabset .tabset-fade}
### Bisnode
```{r}


#dygraph(economic_sentiment,group = "keywords")%>%
 # dyAxis("x", drawGrid = FALSE)%>%
  #dySeries("value", label = "Index")%>%
 # dyEvent(events$date, events$event, labelLoc = "bottom") %>%
 # dyRangeSelector(dateWindow = c("2006-01-01", today))%>%
 # dyOptions(useDataTimezone = TRUE)
```
### Manufacturing

```{r}

```

### Services

###### Description

The sentiment indicator for the *Perceived Economic Situation* consists of Google search terms that aim to reflect people's concerns about the current economic situation. For instance, people might search for "Wirtschaftskrise" (= economic crisis) to get information.  

###### Keywords

- economic crisis ("Wirtschaftskrise")
- short-term work ("Kurzarbeit)
- unemployed ("arbeitslos")
- insolvency ("Insolvenz")

[Download data](https://raw.githubusercontent.com/anneval/MA_data/main/raw/at/trendecon_sa.csv){target="_blank"}
