---
title: "Assignment 3 - Finding fast growing firms"
subtitle: "Course: ECBS6067 - Prediction with Machine Learning for Economists"
author: "Anja Hahn, Teresa Huebel & Anne Valder" 
date: "2023-12-14"
editor_options:
  markdown:
    wrap: 72
output: pdf_document
always_allow_html: true
df_print: paged
---

### Summary

The goal of our analysis is to classify fast growing firms in order to
identify lucrative investment opportunities. This report includes three
different models to predict fast growing firms. It is based on the bisnode
panel data. Firm growth is defined by average annual percentage growth
in sales over two years. We use data from 2012 to predict sales growth
two years ahead. The models are a logit, a random forest and a logit lasso.
The models' predictive power is evaluated once without and once with the
use of a loss function. After the introduction of a loss function, we
identified the random forest as strongest model. This model is also used on
the subsets manufacturing and services. In comparison, the random forest 
performs better in the services sector. Further results and interactive graphs can be found in the felxdashbaord linked to this report.


```{r setup, include=FALSE}
# Set options for markdown
knitr::opts_knit$set(root.dir = 'C:/Users/AnjaHahn/OneDrive - DataScience Service GmbH/WU/Courses/CEU Prediction with Machine Learning for Economists/da_case_studies')

# output folder from which to source graphs and tables
output <- "output/"

knitr::opts_chunk$set(fig.align = 'center', warning = FALSE, message = FALSE, echo = FALSE)

# store different directories here:
# C:/Users/thuebel/OneDrive - WU Wien/Docs/06 Courses and Study/02 Prediction with ML for Economists/da_case_studies
# C:/Users/avalder/OneDrive - WU Wien/Documents/Study/WS_23_24/Pred_MLE_Econ/da_case_studies
# C:/Users/AnjaHahn/OneDrive - DataScience Service GmbH/WU/Courses/CEU Prediction with Machine Learning for Economists/da_case_studies

library(gridExtra)
library(kableExtra)

```


### Sample Design

We exclude some variables that have extremely high rates of missing
values (above 90%) and only look at firms that are active in 2012, i.e. have some sales. What is more, our analysis is only based on
firms with annual sales between 1,000 and 10 million euros. We believe
this subset presents the most attractive investment opportunities.
First, very small firms with sales below 1,000 EUR in sales are likely
not to seek investment and high growth events might happen at random
more easily. Second, very large firms are well represented in various
indices and any expected growth is likely to be already incorporated in
the stock price. Hence, our sample selection represents a business
decision to focus on a segment that is more predictable and more
promising for investors.

### Label Engineering

We are exploring multiple alternatives as target variable to represent
high growth firms. In our selection, we pay attention to the following
dimensions: i) the indicator to choose, ii) the measurement, iii) the
time horizon, and iv) the threshold. The literature does not yield one
consensus over a definition of high growth firms, it rather points out
that any decision along these dimensions depends on the goal of the
analysis.[^1] We decided for relative average annual sales growth over
two years for the following reasons: First, sales provided a more
relevant and reliable target than number of employees. Sales data is
missing only in 2.6% of cases whereas number of employees is missing in
50.9% of cases. Also, sales growth is more closely linked to higher
profits. What is more, 85% of firms had less than 1 employee on average.
Second, we decided to use relative growth instead of absolute growth.
This decision will favor smaller firms since high relative growth is
harder to achieve for larger firms. We believe relative growth to be
more relevant since it is more closely linked to our expected return on
investment. To be more specific, we calculated the percentage change and did
not rely on log differences. Even though this decision does not affect
the ranking of firms, it does affect the magnitude of the growth rate in
the subset of high growth firms. The difference is visualized in a plot that
shows the distribution of growth rates for both measures, where log-differences are right-skewed. 

```{r plot sales growth, include=TRUE, echo=FALSE, fig.align='center', fig.height=2.5, fig.width=8}
plot_sales_growth_both <- readRDS(paste0(output, "plot_sales_growth_both.RDS"))
plot_sales_growth_both
```


We favored percentage change primarily because of
its more intuitive interpretation. Third, we decided for a two year time
horizon instead of a one year horizon to relate more closely to the OECD
definition of high growth firms (HGF) that is defined over a three year
horizon. Fourth, we decided for a threshold of 30% annual growth. In our
sample this is equivalent to classifying roughly the fastest growing 20%
of firms as HGF. In the literature, both thresholds on a certain growth
rate and a certain percentile of firms are used. We decided for a
threshold based on a specific growth rate since we want to analyze
different sectors (manufacturing and services) with a fixed benchmark.

[^1]: Alex Coad, Sven-Olov Daunfeldt, Werner Hölzl, Dan Johansson, Paul
Nightingale, High-growth firms: introduction to the special section,
Industrial and Corporate Change, Volume 23, Issue 1, February 2014,
Pages 91--112, <https://doi.org/10.1093/icc/dtt052>

### Feature Engineering

The feature engineering process includes plausibility checks: As some of
our financial variables (e.g. *inventories*, *fixed_assets* etc.) must
not be negative, we flag them and set negative values to zero. Other
implausible variables, such as *ceo_age* below 18 years, we set to NA.

In the process of analysing missing values, we impute some important
ones (*ceo_age*, *labor_avg*) and add flags for missing values. For
other, important variables (mainly assets, CEO and industry
information), we do not impute but rather drop NAs. Moreover,
we intend to use the variable on previous firm growth as predictor for
(future) fast growth -- very much in the same fashion as we know from
time trend models. Thus, we include the lagged growth in sales (2011 to
2012). As this results in some NAs (due to some missing sales values in
2011), we again flag the observations concerned and impute them by
replacing them with 0. This means we assume that said observations did
not experience any growth. Although this solution is not ideal, it is
based on the assumption that we compare a firm's (missing) sales value
in 2011 to the value of its "nearest neighbour" -- the firm's sales in
2012.

Moreover, we compute some new variables: *age* of the company, a dummy
for whether it is a *new* company, has *multiple_ceo*s or a
*foreign_management*. We classify the observations based on their
two-digit NACE codes into "manufacturing" vs. "services", generate a 
variable for *total_assets* and compute ratios of
some financial variables (with either *total_assets* or *sales* as
reference). Lastly, we winsorize tails of numeric variables and add
flags accordingly.

Next, we look at relationships between predictors and the binary
response. We use the LOESS (locally estimated scatterplot smoothing)
method to fit a smooth curve to the data points. In case the curve shows
some clear non-linear behaviour, we add quadratic terms of predictors
concerned. These decisions are re-assured by the estimation of simple
GLMs, where we explain *high_growth* with the respective numeric
variable and its quadratic term -- whenever we detect a statistically
significant relationship between a quadratic term and the binary
response, we add that variable as quadratic predictor as well. From
visual inspection of the plots, we can say that in general, asset
variables do not show a lot of variation in the response i.e. do not
seem to affect *fast_growth* as much.

Moreover, we looked at the relationship between the binary response and
binary/categorical predictors. In the left plot below, we see, for example,
that *high_growth* seems to be more prevalent with a young (defined as
\< 40 years) CEO. Also, a firm being very young (\< 1 age) seems to play
a role. Regarding possible interactions, the below right plot hints towards a relationship between industry category (NACE 2 digit classification) and
age of the company, as can be seen by the different slopes of the fitted
line per category.

```{r plots relation 2, include=TRUE, echo=FALSE, fig.align='center', fig.height=2.5, fig.width=9}

high_growth_new <- readRDS(paste0(output, "high_growth_new.RDS"))
high_growth_young <- readRDS(paste0(output, "high_growth_young.RDS"))
high_growth_ind2 <- readRDS(paste0(output, "high_growth_ind2.RDS"))

grid.arrange(high_growth_new, high_growth_young, high_growth_ind2, ncol = 3)

```

### Variable Selection

#### Logit Model

For the logit, we try out two specifications. Both of them include the
sales variable (past growth), engineered variables (i.e. ratios of
financial variables, windsorized), the detected (possible) quadratic
terms and the flags we created for extreme, missing and potentially
erroneous data. Also, both specifications include quality variables
(balance sheet information) and information on HR (e.g. CEO information)
and the firm itself (e.g. regarding the location). The
difference lies in interactions included: Whilst the first specification
does not include any interactions, the second one interacts selected
variables with the industry variable. 

#### Probability Forest

Since the probability forest can deal with complicated relationships
between variables, we do not include any quadratics, interacted,
modified and/or windsorized variables. Thus, the raw financial, quality,
sales, HR and firm variables are added. Also, potentially highly
correlated variables are considered together. Categorical variables are
encoded as factors. 

#### LASSO Logit

For the LASSO logit, we consider the same variables as in the second
logit specification (including one additional highly correlated
variable).

### Model Estimation

We divide our data set into a work (80 percent, 15,229 observations) and
holdout set (20 percent, 3,807 observations). The workout set will be
used to train our models. We use 5-fold cross validation to evaluate
performance of our models.


#### Probability Prediction

The table below shows the results for our different model specifications.
We would choose the first simple logit model over the second, since it
has fewer coefficients and even better (lower) RMSE and (higher) AUC.
The logit LASSO does not perform better, either (worse AUC and similar
RMSE). Based on the CV results, we would therefore select the random
forest which performs slightly better in both the RMSE and AUC.

```{r summary_no_loss, include=TRUE, echo=FALSE}
summary_no_loss_table <- readRDS(paste0(output, "summary_no_loss_table.RDS"))
summary_no_loss_table

```

We use our best model to predict on the holdout set and receive a RMSE
of **0.372**. Also, we produce the below (discrete) ROC plot which shows
the trade off between making false positive and false negative
errors. 

```{r best_model_no_loss, include=TRUE, echo=FALSE, fig.align='center',  fig.height=2.5, fig.width=8}

discrete_roc_plot <- readRDS(paste0(output, "discrete_roc_plot.RDS"))
discrete_roc_plot

```


```{r best_model_no_loss1, include=TRUE, echo=FALSE}
cf1_kable <- readRDS(paste0(output, "cf1_kable.RDS"))
cf1_kable
```

When comparing the above confusion matrix (default classification of 0.5 as threshold) to the one below -- where we set the threshold to the mean of predicted values (approx. 0.2) -- we see, as expected,  how a lower threshold would lead to a higher probability of predicting high growth. 
Also, we nicely see the trade-off between false positives (going up) and false negatives 
(going down) when lowering the threshold. However, these choices of thresholds
are still not based on a proper loss function, to which we will come
next.

```{r best_model_no_loss2, include=TRUE, echo=FALSE}

cf2_kable <- readRDS(paste0(output, "cf2_kable.RDS"))
cf2_kable
```

#### Introduction of Loss Function

We introduce a loss function specifically tailored for our business case. In selecting the best model, our primary objective is to minimize false positives. This is crucial because we aim to avoid investing in firms that do not exhibit strong growth potential. However, there's a challenge: only 20% of firms in our data set are categorized as fast-growing. Overemphasizing the cost of false positives could inadvertently lead the model to classify all observations as low growth. Such an approach would undermine our goal of identifying high-potential business opportunities.

To address this, we have calibrated the cost associated with false positives (FP) and false negatives (FN) in a balanced manner. We have set the cost of a false positive at 150% of that of a false negative. This ratio reflects a strategic decision: while avoiding unfruitful investments is important, we also do not want to miss out on promising firms. Additionally, we have incorporated the prevalence of high-growth firms into the model's weighting system. This adjustment ensures that our model remains sensitive to the relatively scarce yet valuable high-growth opportunities in our data set, thereby aligning the model's predictions more closely with our business objectives.

#### Model Comparison with Loss Function
After the introduction of our loss function, we can now compare the models based on their average expected loss over all folds. The model with the lowest expected loss is still the random forest. The simple logistic regression without interactions has the second lowest expected loss.


```{r, include=TRUE, echo=FALSE}
summary_all_mods_kable <- readRDS(paste0(output, "summary_all_mods_kable.RDS"))
summary_all_mods_kable
```

#### Confusion Table
The confusion table shows that we have an accuracy of 82.03% on the holdout set. The model only predicts 1.65% of models to have high growth whereas the prevalence of high growth firms in the data is 18.57%. This low sensitivity (6%) is necessary in order to arrive at the high specificity (99.3%) we desire. This is a trade off we are willing to engage in, in order to avoid investing in firms that will not outperform the market or might even go bankrupt. If we apply our model to similar data sets in multiple countries we will still arrive at a reasonably large number of predicted high growth firms such that our portfolio will be diversified. 

Of course, we realize that we could not test the external validity of our model and applying it in other countries might lead to worse performance. To that end, we conduct another exercise and apply our model to different market segments, that is, manufacturing and services.

#### Comparison of models in manufacturing and services
The random forest performs better in the services sector. It exhibits a lower RMSE, a higher AUC and a lower expected loss. 

```{r include table manu serv, echo=FALSE, include=TRUE}

summary_manu_serv_kable <- readRDS(paste0(output, "summary_manu_serv_kable.RDS"))
summary_manu_serv_kable
```

More differences can be seen in the respective confusion tables. First, manufacturing exhibits a higher prevalence of high growth firms (20.6% versus 17.6%).
Nevertheless, the model performs slightly better in predicting high growth firms in services. In this sector it exhibits a lower false positive rate which is our main goal. (However, it has a higher false negative rate). Notably, the false positive rate in our holdout set is basically at zero, meaning we classified (almost) no firm in the services sector as fast growing that did not turn out to become a high growth firm. This finding points to the services industry as an attractive market albeit its lower average growth rates. It seems to be the case that the characteristics of firms in services make their future growth quite predictable.

```{r include cf matrix manu, echo=FALSE, include=TRUE}

cm5_perc_kable <- readRDS(paste0(output, "cm5_perc_kable.RDS"))
cm5_perc_kable
cm6_perc_kable <- readRDS(paste0(output, "cm6_perc_kable.RDS"))
cm6_perc_kable

```


### Variable Importance

As a last task, we looked at some methods to interpret our random forest probability model. These visualizations can be found in an interactive dashboard we set up (see Dashboard.rmd in github folder, incl. README).  

All in all, we are confident that our model points us to some of the firms with the highest growth potential and believe it to be a valuable tool for predicting high growth firms. At the same time, we realize that our high specificity comes at the cost of a low sensitivity. This means that we will miss many other high growth firms.
